Speed estimation for vehicles using \\SVM classification and edge detection

### 2016-06-15 Administratie/report/paper.tex
Finishing up

\documentclass[runningheads,a4paper]{llncs}
\usepackage[english]{babel}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{booktabs}
\usepackage{float}

@@

\begin{abstract}
This is the abstract: The goal of this paper it to determine the maximum speed for a moving vehicle in traffic, using only camera images and information from the steering column. We construct a system that combines SVM classification and edge detection to foresee possible obstacles on the given trajectory of the car. The maximum speed is computed so that braking in time will avoid collision with those obstacles. 
TODO: hoe goed is dit systeem?
\keywords{SVM classification, Local Binary Patterns, edge detection}
\end{abstract}

@@

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig/RBF_Col_wi_RM.png}
\caption{F-scores for color with road marks using RBF kernel}
\label{fig:col-wi-rm}
\end{figure}

@@

\textbf{TODO} grafiek wo/wi RM

@@

TODO figure aanpassen
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{fig/16_wi_roadmarks.png}
\caption{Comparision of F-scores for 16x16px block size with road marks using RBF kernel }
\label{fig:16_wi_roadmarks}
\end{figure}

@@

\textbf{TODO} check if list not f***ed up.\\
\noindent In retrospect, the optimal parameters for our classification problem are:
\begin{itemize}
\item RBF kernel
\item Block size 32x32px
\item Using only color histogram values for the feature vectors
\item Including road marks as part of the road  
\end{itemize}

@@

>>>>

\documentclass[runningheads,a4paper]{llncs}
\usepackage[english]{babel}
\usepackage{appendix}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{booktabs}
\usepackage{float}

@@

\begin{abstract}
The goal of this paper it to determine the maximum speed for a moving vehicle in traffic, using only camera images and information from the steering column. We construct a system that combines SVM classification and edge detection to foresee possible obstacles on the given trajectory of the car. The maximum speed is computed so that braking in time will avoid collision with those obstacles. 
TODO: hoe goed is dit systeem?
\keywords{SVM classification, Local Binary Patterns, edge detection}
\end{abstract}

@@

All of these results for the classifier can be found in appendix \ref{appendix}.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig/RBF-COL-wi-RM.pdf}
\caption{F-scores for color with road marks using RBF kernel}
\label{fig:col-wi-rm}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{fig/16-wi-roadmarks.pdf}
\caption{Comparision of F-scores for 16x16px block size with road marks using RBF kernel }
\label{fig:16_wi_roadmarks}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig/with-vs-without-roadmarks.pdf}
\caption{F-scores for 16x16px blocks with color using RBF kernel}
\label{fig:col-wi-rm}
\end{figure}

@@

\noindent In retrospect, the optimal parameters for our classification problem are:
\begin{itemize}
\item RBF kernel
\item Block size 32x32px
\item Using only color histogram values for the feature vectors
\item Including road marks as part of the road  
\end{itemize}

@@

\newpage
\appendix
\section{F-scores of parameter iterations}
\label{appendix}

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{fig/RBF-LBP-wo-RM.pdf}
\caption{F-scores for LBP without road marks using RBF kernel}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{fig/RBF-COL-wo-RM.pdf}
\caption{F-scores for color without road marks using RBF kernel}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.85\textwidth]{fig/RBF-LBP-COL-wi-RM.pdf}
\caption{F-scores for LBP and color without road marks using RBF kernel}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.85\textwidth]{fig/RBF-LBP-wi-RM.pdf}
\caption{F-scores for LBP with road marks using RBF kernel}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.85\textwidth]{fig/RBF-COL-wi-RM.pdf}
\caption{F-scores for color with road marks using RBF kernel}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.85\textwidth]{fig/RBF-LBP-COL-wi-RM.pdf}
\caption{F-scores for LBP and color with road marks using RBF kernel}
\end{figure}
